\section{Player interviewing}
\label{sec:player-interviewing}

After the players completes the game, they will be prompted with a survey
about their experience. This survey aims to provide insight as to what
the players have obtained from the experience, and wether if they
think about taking further action thanks to the knowledge obtained from it, 
aswell as gathering feedback about the technical quality of the game.

The questions have been deliberately kept short and few as to maximize player
engagement with it.

In section \ref{sec:survey-questions} all of the survey questionst can be read.

\subsection{Survey questions}\label{sec:survey-questions}

\paragraph{Game experience}
Questions related to gameplay and entertainment.

\begin{enumerate}
\item I hold my experience with the game to have been an entertaining one.
\item I noticed that the game was finished, complete and free of bugs.
\end{enumerate}

\paragraph{Game premise}
ReWild is a game about the environment. In this case, we've chosen to focus on meat consumption and its harmful impact on the planet versus meat alternatives.

\begin{enumerate}
\item I understood the game's premise through its mechanics.
\item I think ReWild is a good metaphor for exploring the premise.
\end{enumerate}

\paragraph{Reflections}
Questions about reflections that the game prompted upon the player's behaviours.

\begin{enumerate}
\item The game has made me reevaluate my relationship with nature and i'm considering taking action in response to it.
\end{enumerate}
