\begin{thebibliography}{9}

%\end{thebibliography}
\bibitem{trans}
  Maria Serna,
  \emph{Ampliació d'Algorismia, Class transparencies},
  Fall 2017

\bibitem{vazi01}
  Vijay Vazirani
  \emph{Approximation Algorithms},
  2001, Springer

\bibitem{yan}
  Mihalis Yannakakis
  \emph{A Polynomial Algorithm for the Min-Cut Linear Arrangement of Trees}
  1985, AT\&T Bell Laboratories, Murray Hill, New Jersey 

\bibitem{Garey79}
  Garey, M. R., AND Johnson, D. S. 
  \emph{Computers and Intractability: A Guide to the Theory of NP-completeness.}
  W. H. Freeman, San Francisco, Calif., 1979. 

\bibitem{Gavril77}
  Gavril, F
  \emph{Some NP-complete problems on graphs},
  In Proceedings of the 11th Conference on Information Sciences and Systems. Johns Hopkins University, Baltimore, Md., 1977, pp. 91-95

\bibitem{Len82}
   Lenaguer, T. U
   \emph{Upper and lower bounds on the complexity of the min-cut linear arrangement on trees }
   Siam J. Alg. Disc. Meth. 3 (1982), 99-113
\bibitem{Chu82}
   Chung, M., MAKEDON, F., Sudborough, .I.H. and Turner, J.
   \emph{Polynomial tile algorithms for the min cut problem on degree restricted trees}
   Proceedings of the 23rd Annual Symposium on the Foundations of Computer Science. IEEE, New York, 1982, pp. 262-271	

\bibitem{MS85}
 Monien, B. and Sudborough, I. H. 
 \emph{Min Cut is NP-complete for Edge Weighted Trees}
 Unpublished manuscript (1985)

\bibitem{Ma82}
 Makedon, F.
 \emph{Layout Problems and Their Complexity}
 Ph.D. Thesis, EECS Department, Northwestern University (1982)

\end{thebibliography}
