\chapter{Applied knowledge of specialty subjects}

For this project, several competences from various subjects of the Computation
specialty have been applied to it. Below it can be seen a brief description
of said subjects, its competences and how they relate to the project.

\section {Artificial Intelligence (IA)}

\say{Artificial intelligence is a multi-disciplinary science that combines concepts and methods from diverse areas such as mathematics, computer science, philosophy, psychology and biology. Its main objective is to provide computer systems with characteristics or behaviors that simulate intelligence.}
\footnote{https://www.fib.upc.edu/en/studies/bachelors-degrees/bachelor-degree-informatics-engineering/curriculum/syllabus/IA}

\paragraph{Objective 3: Learn different problem-solving techniques based on search (CCO 2.2)} 
This objective aims to tech the student about local search problems and efficient ways to solve them.
This knowledge is applied in this project to obtain efficient pathfinding solutions
for the game logic.

\section{Programming Languages (LP)}

\say{Programming languages are the basic tool in many of the activities made by a computer engineer. Due to this, knowing how to choose the most appropriate programming language in a given situation is crucial.}\footnote{https://www.fib.upc.edu/en/studies/bachelors-degrees/bachelor-degree-informatics-engineering/curriculum/syllabus/LP}

\paragraph{Objective 4: Distinguish the main features of a given programming language. Identify its strengths and weaknesses and be able to justify a choice. (CCO 1.2, G 4.3)} 
This objective gives the student the needed tools to critically pick the programming language that best suits them.

\section{Graphics (G)}

\say{The course focuses on the development of interactive computer graphics applications. The course covers rendering, interaction, and realism techniques. Students will develop 3D applications using C++, OpenGL and GLSL.}\footnote{https://www.fib.upc.edu/en/studies/bachelors-degrees/bachelor-degree-informatics-engineering/curriculum/syllabus/G}

\paragraph{Understand in depth the various stages of the graphics pipeline (CCO 2.6, CT 1.2A, CT 1.2C)}
A knowledge of the graphics pìpeline is basic for building a videogame, especially for a platform that needs optimisation in it.

\paragraph{Assimilating the functionality, programming and execution model shaders in GLSL (CCO 2.6, CT 1.2)}
GLSL is vital for programming shaders and needed visual effects for the engine of choice.

\paragraph{Know the role of computer graphics in the development of software with clear social, economic or environmental contributions, in fields such as medicine, industrial design and cultural heritage (G 2.3)}
Knowledge about the ramifications of graphics for environmental purposes is very tied with this project's objectives.
