\chapter{List of technical competences chosen}


\paragraph{CCO1.1: Avaluar la complexitat computacional d'un problema, conèixer estratègies algorísmiques que puguin dur a la seva resolució, i recomanar, desenvolupar i implementar la que garanteixi el millor rendiment d'acord amb els requisits establerts. [A little bit]}
This competence needed in order to ensure that the videogame runs smoothly
on mobile devices. The implication on this competence is relatively low
because it is not the main focus of the project to solve technical issues of
efficiency, but rather use efficiency as a way for the project to attain a
fairly high degree of complexity without generating much stress over the
machine's resources.

\paragraph{CCO2.3: Desenvolupar i avaluar sistemes interactius i de presentació d'informació complexa, i la seva aplicació a la resolució de problemes de disseny d'interacció persona computador. [Enough]}
A high degree of understanding of information display and computer human interaction
is one of the main focuses of this project. A great ammount of development
time will be devoted to find solutions to transmit complex ideas through
computer graphics.

\paragraph{CCO2.6: Dissenyar i implementar aplicacions gràfiques, de realitat virtual, de realitat augmentada i videojocs. [In depth]}
As the main objective of this project is to build a mobile video game, this
competence will be developed extensively, and will be the cornerstone of
the whole project. All knowledge gatered on this field will be used for building
the best possible solution according to the project's objectives.

